Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-12 paper.tex
ADD bib

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.45in]{geometry}
\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

\begin{abstract}
Campbell and Yogo (2006) propose a Bonferroni-type procedure for valid inference of predictive regressions with almost nonstationary regressors. In this study, I will explain the rationale behind their method, replicate empirical findings, and extend them with out-of-sample data that surfaced since their method's publication. Further, I will investigate via Monte Carlo simulation the method's behavior when its assumptions are violated in ways likely encountered in practice. 
\end{abstract}

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. Elliott and Stock (1994) find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, Campbell and Yogo (2006) develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of the Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in section $\ref{Infeasible tests}$. This section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by Campbell and Yogo (2006). Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in section $\ref{implementation}$. First, Monte Carlo evidence of Campbell and Yogo (2006) is scrutinized and replicated in section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovation variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in section $\ref{Empirical Results}$. Finally, section $\ref{conclusion}$ concludes.

\section{The regression setup and its problem}
\label{regression}
With log-returns $r_{t}$ observable at time $t$ and lagged supposedly predictive variable $x_{t-1}$ observable at $t-1$,  Campbell and Yogo (2006) consider the regression system
\begin{align} 
\label{eqn:1}
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
\label{eqn:2}
x_{t} = \gamma + \rho  x_{t-1} + e_{t}.
\end{align}
They further assume normality, i.e., 
\begin{equation}
w_{t}=\left(u_{t}, e_{t}\right)^{\prime} \stackrel{i i d}{\sim} \mathrm{N}(\boldsymbol{0}, \boldsymbol{\Sigma})
\end{equation} where  $\boldsymbol{\Sigma}=\left[\begin{array}{cc}{\sigma_{u}^{2}} & {\sigma_{u e}} \\ {\sigma_{u e}} & {\sigma_{e}^{2}}\end{array}\right]$ is known.

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A common approach is to perform a t-test of $\beta$. Elliott and Stock (1994), however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being greater than some deemed-acceptable nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, Campbell and Yogo (2006) start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

To reason about how to incorporate information about $\rho$ into the test Campbell and Yogo (2006) assume $\rho$ to be known at first. If, further, the assumption $\alpha=\gamma=0$ is made, the only unknown variable that remains is $\beta$. Now, the likelihood function can be denoted as $L(\beta)$. If one restricts oneself to consider only the simple alternative of the form $\beta=\beta_{1}$ one can reason by the Neyman–Pearson Lemma that the most powerful test is of the form
\begin{equation}
\begin{aligned} \sigma_{u}^{2}\left(1-\delta^{2}\right)\left(L\left(\beta_{1}\right)-L\left(\beta_{0}\right)\right)=& 2\left(\beta_{1}-\beta_{0}\right) \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right] \\ &-\left(\beta_{1}^{2}-\beta_{0}^{2}\right) \sum_{t=1}^{T} x_{t-1}^{2}>C, \end{aligned}
\end{equation}
with $\beta_{u e}=\sigma_{u e} / \sigma_{e}^{2}$ and $C$ being some constant.
This optimal test is not uniformly most powerful [UMP], however, since it is a weighted sum of minimal sufficient statistics and the weights depend on $\beta_{1}$. For that reason, Campbell and Yogo (2006) propose to condition the test on the ancillary statistic  $\sum_{t=1}^{T} x_{t-1}^{2}$. As a result the test can be simplified to
\begin{equation}
 \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]>C,
\end{equation}
which is UMP for alternatives of the form $\beta_{1}>\beta_{0}$ when $\rho$ is known.

For the test-statistic to have a standard normal distribution under the null, Campbell and Yogo (2006) propose to recenter and rescale it, which results in 
\begin{equation}
\frac{\sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{2}\right)^{1 / 2}}>C.
\end{equation}
Revoking the previous assumption of $\alpha=\gamma=0$ and generalizing instead to any unknown  $\alpha$ and $\gamma$ by replacing $x_{t-1}$ by its demeaned value $x_{t-1}^{\mu}$, the test
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}}>C
\end{equation}
is UMP conditional on $\sum_{t=1}^{T} x_{t-1}^{\mu 2}$.
This Q-statistic, as Campbell and Yogo (2006) call it, has an intuitive interpretations when $\beta_{0} = 0$. It is the t-statistic of the $\beta^{\star}$ coefficient in the regression
 \begin{equation}
 \label{eqn:r_star}
r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)=\alpha^{\star}+\beta^{\star} x_{t-1}+v_{t}. 
\end{equation}
Regression ($\ref{eqn:r_star}$) can be interpreted as regressing the de-noised returns onto the regressor $x_{t-1}$, where the information contained in $\rho$ and the correlation of the shocks is exploited.
When $\beta_{u e}=0$, i.e., the correlation of the shocks is zero, the Q-statistic simplifies to the t-statistic which converges to a standard-normal distribution in this case. When $\beta_{u e}\neq0$, the t-statistic does not converge to a standard normal distribution. Instead, as shown by Elliott and Stock (1994), under local-to-unity asymptotic theory it has the null distribution 
\begin{equation}
\label{lua_t}
t\left(\beta_{0}\right) \Rightarrow \delta \frac{\tau_{c}}{\kappa_{c}}+\left(1-\delta^{2}\right)^{1 / 2} Z,
\end{equation}
where $\left(W_{u}(s), W_{e}(s)\right)^{\prime}$ is a two-dimensional Wiener process with correlation $\delta$, $J_{c}(s)$ is defined by $\mathrm{d} J_{c}(s)=c J_{c}(s) \mathrm{d} s+\mathrm{d} W_{e}(s)$ with $J_{c}(0)=0$, $Z$ is a standard normal random variable independent of $\left(W_{e}(s), J_{c}(s)\right)$, $\kappa_{c}=\left(\int J_{c}^{\mu}(s)^{2} \mathrm{d} s\right)^{1 / 2}$, and $\tau_{c}=\int J_{c}^{\mu}(s) \mathrm{d} W_{e}(s)$.

@@

\subsection{A pretest}
\label{pretest}
From equation ($\ref{lua_t}$) it's easy to see that if $\delta = 0$, the nuisance term $\delta \frac{\tau_{c}}{\kappa_{c}}$ vanishes and the t-statistic collapses to the standard normal random variable $Z$. It therefore makes sense to test whether $\delta$ is different from zero. If it isn't, one can infer that the t-statistic is approximately standard normal and inference based on it is valid. This, however, is not the only condition in which there is no size distortion. Phillips (1987) shows that if $x_{t}$ is not persistent, $\tau_{c} / \kappa_{c}$ converges to a different standard normal random variable $Z^{\star}$. Hence the t-statistic, as a sum of two independent standard normal random variables, is likewise standard normal.

Campbell and Yogo (2006) use these facts as bases for a pretest. This test supposes that an actual size $\alpha^{\star}  \geq \alpha$ may be acceptable if its not much greater than the nominal size $\alpha$. It then tests whether $\alpha^{\star}$ is greater than a prespecified acceptable size. It would be tempting to use a unit root test and infer no size distortion if its null of nonstationarity can be rejected. Elliott and Stock (1994) show, however, that this does not guarantee valid inference via the t-statistic. Instead, Campbell and Yogo (2006) use a unit root test statistic to construct a confidence interval for $c$ by inverting its alternative distribution in the spirit of Stock (1991). $\delta$, on the other hand, can be consistently estimated from the residuals of regressions ($\ref{eqn:1}$, $\ref{eqn:2}$). The size of the t-statistic forms a two-dimensional surface in the $c$-$\delta$-parameter space. If the confidence interval for $c$ lies strictly outside the region where the size is above the acceptable threshold for $\hat{\delta}$, the null of unacceptable size distortion can be rejected. This test is implemented with tables provided by Campbell and Yogo (2006), who use the DF-GLS test statistic proposed by Elliott et al. (1996) to construct the confidence interval for $c$. The application accompanying uses the closest tabulated values to the estimated values without interpolating.

@@

When the pretest cannot reject the null of unacceptable size distortion inference cannot be based the t-test without adjustment. While the Q-test is UMP when $\rho$ and $\delta$ are known, in practice this is not the case. Furthermore, $\rho$ cannot be estimated consistently since its OLS estimator converges at rate $T$. Instead, analogously to the description in the previous section, Campbell and Yogo (2006) construct a $100\left(1-\alpha_{1}\right) \%$ confidence interval, $C_{\rho}\left(\alpha_{1}\right)$ for $\rho$ from a unit root test statistic. They then construct $C_{\beta | \rho}\left(\alpha_{2}\right)$, a $100\left(1-\alpha_{2}\right) \%$ conditional on $\rho$ confidence interval for $\beta$. To marginalize $\rho$ and thus getting an unconditional confidence interval for $\beta$ they take the union over $\rho \in C_{\rho}\left(\alpha_{1}\right)$

@@

If this confidence interval does not contain zero, the regressor is inferred to have predictive power. While this test is valid, it is conservative, however, since Bonferroni's inequality is likely to be strict, i.e., the coverage of $C_{\beta}(\alpha)$ is likely greater than $100(1-\alpha) \%$. For that reason, Campbell and Yogo (2006) refine the confidence interval based on a numerical method proposed by Cavanagh et al. (1995). To obtain a tighter confidence interval with significance level $\widetilde{\alpha}$, according to this method, $\alpha_{2}$ is fixed first. $\operatorname{Pr}\left(\underline{\beta}\left(\overline{\rho}\left(\overline{\alpha}_{1}\right), \alpha_{2}\right)>\beta\right)$ is then evaluated for each $\delta$, and $\overline{\alpha}_{1}$ is selected such that 

@@

As argued by Phillips (2014), the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

Campbell and Yogo (2006) evaluate the robustness of the Q-test under a fat-tailed distribution. In particular, they find finite-sample rejection probabilities to be unchanged from the Gaussian case when the innovations follow a Student t-distribution with five degrees of freedom. As shown by Cavaliere (2004), unit root tests may be invalid under conditional heteroskedasticity. Assumptions in the form of equation ($\ref{eqn:covarst}$) imply validity of the Q-test under conditionally heteroskedastic innovations only if they are covariance stationary. 

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.45in]{geometry}
\usepackage[round]{natbib}

\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

\begin{abstract}
\citet{campbell2006efficient} propose a Bonferroni-type procedure for valid inference of predictive regressions with almost nonstationary regressors. In this study, the rationale behind their method is explained. Empirical findings are replicated and extended with out-of-sample data that emerged since the method's publication. Furthermore, the method's behavior is investigate via Monte Carlo simulation, highlighting practically relevant scenarios where it over-rejects the null hypothesis of no predictability. 
\end{abstract}

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. \citet{elliott1994inference} find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, \citet{campbell2006efficient} develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of the Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in section $\ref{Infeasible tests}$. This section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by \citet{campbell2006efficient}. Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in section $\ref{implementation}$. First, Monte Carlo evidence of \citet{campbell2006efficient} is scrutinized and replicated in section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovation variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in section $\ref{Empirical Results}$. Finally, section $\ref{conclusion}$ concludes.

\section{The regression setup and its problem}
\label{regression}
With log-returns $r_{t}$ observable at time $t$ and lagged supposedly predictive variable $x_{t-1}$ observable at $t-1$,  \citet{campbell2006efficient} consider the regression system
\begin{align} 
\label{eqn:1}
r_{t} = \alpha + \beta x_{t-1} + u_{t} \\ 
\label{eqn:2}
x_{t} = \gamma + \rho  x_{t-1} + e_{t}.
\end{align}
They further assume normality, i.e., 
\begin{equation}
w_{t}=\left(u_{t}, e_{t}\right)^{\prime} \stackrel{i i d}{\sim} \mathrm{N}(\boldsymbol{0}, \boldsymbol{\Sigma})
\end{equation} where  $\boldsymbol{\Sigma}=\left[\begin{array}{cc}{\sigma_{u}^{2}} & {\sigma_{u e}} \\ {\sigma_{u e}} & {\sigma_{e}^{2}}\end{array}\right]$ is known.

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A common approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being greater than some deemed-acceptable nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

\section{Derivation of the tests}
\label{Derivation of the tests}
\subsection{Infeasible tests}
\label{Infeasible tests}
In developing their test, \citet{campbell2006efficient} start by considering the t-statistic 
\begin{equation}
t\left(\beta_{0}\right)=\frac{\widehat{\beta}-\beta_{0}}{\sigma_{u}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{-1 / 2}},
\end{equation}
where $x_{t-1}^{\mu}=x_{t-1}-T^{-1} \sum_{t=1}^{T} x_{t-1}$ denotes the demeaned regressor and $\widehat{\beta}$ is the OLS estimate of $\beta$. They argue that this test ignores information contained in the system ($\ref{eqn:1}$, $\ref{eqn:2}$) and can thus not be optimal. To see this, consider the joint log likelihood function of the system ($\ref{eqn:1}$, $\ref{eqn:2}$)
\begin{equation}
\begin{aligned} L(\beta, \rho, \alpha, \gamma)=&-\frac{1}{1-\delta^{2}} \sum_{t=1}^{T}\left[\frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}}{\sigma_{u}^{2}}-2 \delta \frac{\left(r_{t}-\alpha-\beta x_{t-1}\right)\left(x_{t}-\gamma-\rho x_{t-1}\right)}{\sigma_{u} \sigma_{e}}\right.\\ &\left.+\frac{\left(x_{t}-\gamma-\rho x_{t-1}\right)^{2}}{\sigma_{e}^{2}}\right] \end{aligned}
\end{equation}
and observe that the t-test squared is equal to the likelihood ratio test statistic
\begin{equation}
\max _{\beta, \rho, \alpha, \gamma} L(\beta, \rho, \alpha, \gamma)-\max _{\rho, \alpha, \gamma} L\left(\beta_{0}, \rho, \alpha, \gamma\right)=t\left(\beta_{0}\right)^{2}.
\end{equation}
But this test statistic turns out to be the same if only the marginal log likelihood 
\begin{equation}
L(\beta, \alpha)=-\sum_{t=1}^{T}\left(r_{t}-\alpha-\beta x_{t-1}\right)^{2}
\end{equation}
is used in its computation. Thus the t-test ignores information about $\rho$.

To reason about how to incorporate information about $\rho$ into the test \citet{campbell2006efficient} assume $\rho$ to be known at first. If, further, the assumption $\alpha=\gamma=0$ is made, the only unknown variable that remains is $\beta$. Now, the likelihood function can be denoted as $L(\beta)$. If one restricts oneself to consider only the simple alternative of the form $\beta=\beta_{1}$ one can reason by the Neyman–Pearson Lemma that the most powerful test is of the form
\begin{equation}
\begin{aligned} \sigma_{u}^{2}\left(1-\delta^{2}\right)\left(L\left(\beta_{1}\right)-L\left(\beta_{0}\right)\right)=& 2\left(\beta_{1}-\beta_{0}\right) \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right] \\ &-\left(\beta_{1}^{2}-\beta_{0}^{2}\right) \sum_{t=1}^{T} x_{t-1}^{2}>C, \end{aligned}
\end{equation}
with $\beta_{u e}=\sigma_{u e} / \sigma_{e}^{2}$ and $C$ being some constant.
This optimal test is not uniformly most powerful [UMP], however, since it is a weighted sum of minimal sufficient statistics and the weights depend on $\beta_{1}$. For that reason, \citet{campbell2006efficient} propose to condition the test on the ancillary statistic  $\sum_{t=1}^{T} x_{t-1}^{2}$. As a result the test can be simplified to
\begin{equation}
 \sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]>C,
\end{equation}
which is UMP for alternatives of the form $\beta_{1}>\beta_{0}$ when $\rho$ is known.

For the test-statistic to have a standard normal distribution under the null, \citet{campbell2006efficient} propose to recenter and rescale it, which results in 
\begin{equation}
\frac{\sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{2}\right)^{1 / 2}}>C.
\end{equation}
Revoking the previous assumption of $\alpha=\gamma=0$ and generalizing instead to any unknown  $\alpha$ and $\gamma$ by replacing $x_{t-1}$ by its demeaned value $x_{t-1}^{\mu}$, the test
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}}>C
\end{equation}
is UMP conditional on $\sum_{t=1}^{T} x_{t-1}^{\mu 2}$.
This Q-statistic, as \citet{campbell2006efficient} call it, has an intuitive interpretations when $\beta_{0} = 0$. It is the t-statistic of the $\beta^{\star}$ coefficient in the regression
 \begin{equation}
 \label{eqn:r_star}
r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)=\alpha^{\star}+\beta^{\star} x_{t-1}+v_{t}. 
\end{equation}
Regression ($\ref{eqn:r_star}$) can be interpreted as regressing the de-noised returns onto the regressor $x_{t-1}$, where the information contained in $\rho$ and the correlation of the shocks is exploited.
When $\beta_{u e}=0$, i.e., the correlation of the shocks is zero, the Q-statistic simplifies to the t-statistic which converges to a standard-normal distribution in this case. When $\beta_{u e}\neq0$, the t-statistic does not converge to a standard normal distribution. Instead, as shown by \citet{elliott1994inference}, under local-to-unity asymptotic theory it has the null distribution 
\begin{equation}
\label{lua_t}
t\left(\beta_{0}\right) \Rightarrow \delta \frac{\tau_{c}}{\kappa_{c}}+\left(1-\delta^{2}\right)^{1 / 2} Z,
\end{equation}
where $\left(W_{u}(s), W_{e}(s)\right)^{\prime}$ is a two-dimensional Wiener process with correlation $\delta$, $J_{c}(s)$ is defined by $\mathrm{d} J_{c}(s)=c J_{c}(s) \mathrm{d} s+\mathrm{d} W_{e}(s)$ with $J_{c}(0)=0$, $Z$ is a standard normal random variable independent of $\left(W_{e}(s), J_{c}(s)\right)$, $\kappa_{c}=\left(\int J_{c}^{\mu}(s)^{2} \mathrm{d} s\right)^{1 / 2}$, and $\tau_{c}=\int J_{c}^{\mu}(s) \mathrm{d} W_{e}(s)$.

@@

\subsection{A pretest}
\label{pretest}
From equation ($\ref{lua_t}$) it's easy to see that if $\delta = 0$, the nuisance term $\delta \frac{\tau_{c}}{\kappa_{c}}$ vanishes and the t-statistic collapses to the standard normal random variable $Z$. It therefore makes sense to test whether $\delta$ is different from zero. If it isn't, one can infer that the t-statistic is approximately standard normal and inference based on it is valid. This, however, is not the only condition in which there is no size distortion. \citet{phillips1987towards} shows that if $x_{t}$ is not persistent, $\tau_{c} / \kappa_{c}$ converges to a different standard normal random variable $Z^{\star}$. Hence the t-statistic, as a sum of two independent standard normal random variables, is likewise standard normal.

\citet{campbell2006efficient} use these facts as bases for a pretest. This test supposes that an actual size $\alpha^{\star}  \geq \alpha$ may be acceptable if its not much greater than the nominal size $\alpha$. It then tests whether $\alpha^{\star}$ is greater than a prespecified acceptable size. It would be tempting to use a unit root test and infer no size distortion if its null of nonstationarity can be rejected. \citet{elliott1994inference} show, however, that this does not guarantee valid inference via the t-statistic. Instead, \citet{campbell2006efficient} use a unit root test statistic to construct a confidence interval for $c$ by inverting its alternative distribution in the spirit of \citet{stock1991confidence}. $\delta$, on the other hand, can be consistently estimated from the residuals of regressions ($\ref{eqn:1}$, $\ref{eqn:2}$). The size of the t-statistic forms a two-dimensional surface in the $c$-$\delta$-parameter space. If the confidence interval for $c$ lies strictly outside the region where the size is above the acceptable threshold for $\hat{\delta}$, the null of unacceptable size distortion can be rejected. This test is implemented with tables provided by \citet{campbell2006efficient}, who use the DF-GLS test statistic proposed by \citet{elliott1996efficient} to construct the confidence interval for $c$. The application accompanying uses the closest tabulated values to the estimated values without interpolating.

@@

When the pretest cannot reject the null of unacceptable size distortion inference cannot be based the t-test without adjustment. While the Q-test is UMP when $\rho$ and $\delta$ are known, in practice this is not the case. Furthermore, $\rho$ cannot be estimated consistently since its OLS estimator converges at rate $T$. Instead, analogously to the description in the previous section, \citet{campbell2006efficient} construct a $100\left(1-\alpha_{1}\right) \%$ confidence interval, $C_{\rho}\left(\alpha_{1}\right)$ for $\rho$ from a unit root test statistic. They then construct $C_{\beta | \rho}\left(\alpha_{2}\right)$, a $100\left(1-\alpha_{2}\right) \%$ conditional on $\rho$ confidence interval for $\beta$. To marginalize $\rho$ and thus getting an unconditional confidence interval for $\beta$ they take the union over $\rho \in C_{\rho}\left(\alpha_{1}\right)$

@@

If this confidence interval does not contain zero, the regressor is inferred to have predictive power. While this test is valid, it is conservative, however, since Bonferroni's inequality is likely to be strict, i.e., the coverage of $C_{\beta}(\alpha)$ is likely greater than $100(1-\alpha) \%$. For that reason, \citet{campbell2006efficient} refine the confidence interval based on a numerical method proposed by Cavanagh et al. (1995). To obtain a tighter confidence interval with significance level $\widetilde{\alpha}$, according to this method, $\alpha_{2}$ is fixed first. $\operatorname{Pr}\left(\underline{\beta}\left(\overline{\rho}\left(\overline{\alpha}_{1}\right), \alpha_{2}\right)>\beta\right)$ is then evaluated for each $\delta$, and $\overline{\alpha}_{1}$ is selected such that 

@@

As argued by \citet{phillips2014confidence}, the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of \citet{campbell2005implementing}. Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

\citet{campbell2006efficient} evaluate the robustness of the Q-test under a fat-tailed distribution. In particular, they find finite-sample rejection probabilities to be unchanged from the Gaussian case when the innovations follow a Student t-distribution with five degrees of freedom. As shown by \citet{cavaliere2005unit}, unit root tests may be invalid under conditional heteroskedasticity. Assumptions in the form of equation ($\ref{eqn:covarst}$) imply validity of the Q-test under conditionally heteroskedastic innovations only if they are covariance stationary. 
It is therefore interesting to observe the behavior of the Bonferroni Q-test if innovations are modeled by a generalized autoregressive conditional heteroskedasticity [GARCH] process that approaches covariance nonstationarity. If the regressor is a valuation ratio, it seems sensible that there is a more or less stable correlation between the regressor and stock returns. A multivariate GARCH model that allows such a restriction is the Constant Conditional Correlations GARCH  [CCC-GARCH] model of \citet{bollerslev1990modelling}. It is defined as follows. Let $ \boldsymbol{z_{t}}$ be a bivariate standard normal random variable, i.e., $ \boldsymbol{z}_{t} \stackrel{i i d}{\sim} \mathrm{N}\left(\mathbf{0}, \boldsymbol{I}_{2}\right)$. Then the innovations are modeled as 
